\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

\definecolor{myblue}{RGB}{0, 0, 255}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
\textbf{\Huge \scshape Nadutkin Fedor} \\ \vspace{5pt}
\small +7(904)-221-86-70  $|$ \href{mailto:fedya123452@gmail.com}{\underline{fedya123452@gmail.com}} $|$
\href{https://github.com/FedosOnGIT}{\faGithub \ \underline{github.com/FedosOnGIT}} $|$
\faTelegram \ @OooVelichaishiFedya
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://en.itmo.ru/}{\textcolor{myblue}{ITMO University}}}
{Saint Petersburg, Russia}
{Masters in Programming and Artificial Intelligence}
{Sep. 2023 -- Present}

\resumeSubheading
{\href{https://en.itmo.ru/}{\textcolor{myblue}{ITMO University}}}
{Saint Petersburg, Russia}
{Bachelor’s in Applied Mathematics and Informatics}
{Sep. 2019 -- Aug. 2023}

\resumeSubheading
{\href{https://route256.ozon.ru/go-developer}{\textcolor{myblue}{Route 256}}}{Ozon Company}
{Go Middle Developers Courses}{May 2023 -- Jul. 2023}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Dzen} $|$ \emph{Java, Go} $|$ \emph{Search Team, Text Team, Sport Team} $|$ \href{https://dzen.ru/}{\textcolor{myblue}{Dzen product}}}{July 2023 - Present}

\resumeItemListStart
\resumeItem{Developed specialized search verticals for short videos and mixed content, enhancing search functionality and user engagement.}
\resumeItem{Transitioned Dzen articles and briefs from the outdated draft.js format to the advanced quill delta editor, improving content management efficiency.}
\resumeItem{Coordinated comprehensive coverage of the 2024 Olympic Games within Dzen Sports, significantly increasing user interaction and site traffic.}
\resumeItem{Integrated real-time updates and featured content for major basketball and volleyball tournaments into Dzen Sports News, boosting live event engagement.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{SmartHomeDevices} $|$ \emph{Java, Kotlin} $|$ \emph{Integration with Partners} $|$ \href{https://sberdevices.ru/}{\textcolor{myblue}{The Site of company}}}{May 2022 - July 2023}

\resumeItemListStart
\resumeItem{Developed a tool to accurately extract product attributes such as weight, volume, size, and quantity from product names, enhancing inventory management.}
\resumeItem{Redesigned the showcase generation service, optimizing its performance and improving user experience.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Developer Soft / DevExpress} $|$ \emph{C\#} $|$ \emph{Data Visualization and Analysis} $|$ \href{https://www.devexpress.com/}{\textcolor{myblue}{The site of the company}}}{Aug 2021 - Mar 2022}

\resumeItemListStart
\resumeItem{Designed and implemented \href{https://docs.devexpress.com/CoreLibraries/DevExpress.DataProcessing.Criteria.ICustomAggregateFunction}{\textcolor{myblue}{custom aggregate functions}}, enhancing data processing capabilities.}
\resumeItem{Developed and integrated \href{https://docs.devexpress.com/Dashboard/403867/basic-concepts-and-terminology/bi-dashboard-performance/bi-dashboard-diagnostic-tool?v=22.1}{\textcolor{myblue}{diagnostic collection features}}, improving system monitoring and troubleshooting.}
\resumeItem{Implemented a tree isomorphism algorithm to facilitate the visualization of log trees, aiding in data analysis and debugging.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Bin} $|$ \emph{Bash} $|$ \faGithub~\href{https://github.com/FedosOnGIT/MY\_OS\_Labs/tree/master/lab4}{\textcolor{myblue}{Bin}}}{Dec 2020}

\resumeProjectHeading{\textbf{Big-Integer} $|$ \emph{C++} $|$ \faGithub~\href{https://github.com/FedosOnGIT/first-term/tree/bigint-opt/bigint-optimized}{\textcolor{myblue}{BigInteger}}}{June 2020}

\resumeProjectHeading{\textbf{Concurrent Algorithms} $|$ \emph{Java, Kotlin} $|$ \faGithub~\href{https://github.com/FedosOnGIT/Concurrent-programming}{\textcolor{myblue}{Concurrent Algorithms}}}{Jan 2022}
\resumeItemListStart
\resumeItem{Concurrent-Friendly Skip-List}
\resumeItem{Concurrent HashTable}
\resumeItem{And others...}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Hi Language Interpreter} $|$ \emph{Haskell} $|$ \faGithub~\href{https://github.com/FedosOnGIT/hi}{\textcolor{myblue}{Hi}}}{Jan 2022}

\resumeProjectHeading{\textbf{Distributed Algorithms} $|$ \emph{Kotlin, Java} $|$ \faGithub~\href{https://github.com/FedosOnGIT/Distributed-systems}{\textcolor{myblue}{Distributed Systems}}}{June 2022}
\resumeItemListStart
\resumeItem{Consistent Hashing}
\resumeItem{Raft Consensus Algorithm}
\resumeItem{And others...}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Software Engineering} $|$ \emph{Java, Kotlin} $|$ \faGithub~\href{https://github.com/FedosOnGIT/Software-Engineering/tree/main}{\textcolor{myblue}{Software Engineering}}}{Sep 2022 - Apr 2023}
\resumeItemListStart
\resumeItem{Implemented various programming patterns like reactive programming and event sourcing.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Highload} $|$ \emph{Java} $|$ \faGithub~\href{https://github.com/FedosOnGIT/Highload}{\textcolor{myblue}{Highload}}}{Sep 2022 - Jan 2023}
\resumeItemListStart
\resumeItem{Parallel request processing and async execution server.}
\resumeItem{Sharding and replication.}
\resumeItem{Range requests.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Programming Languages:} Java, Kotlin, Go, SQL, Python, Bash}
\resumeItem{\textbf{Frameworks and Libraries:} Spring Boot, Hibernate, Ktor, Exposed Framework}
\resumeItem{\textbf{Development Tools:} Git, Maven, Gradle, Docker}
\resumeItem{\textbf{Databases and Messaging Systems:} PostgreSQL, MongoDB, Redis, Yandex Database (YDB), Yandex Table (YT), Apache Kafka, Apache Ignite}
\resumeItem{\textbf{Monitoring Tools:} Grafana, Prometheus, Kibana}
\resumeItem{\textbf{Testing Frameworks:} JUnit}
\resumeItem{\textbf{Communication Protocols and Data Formats:} gRPC, JSON}
\resumeItem{\textbf{Database Versioning Tools:} Liquibase, Flyway}
\resumeSubHeadingListEnd

\end{document}
